State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-12 prism-backend/research/soa_review/ac.tex
Comment.
Added summary of ASM06 into related work section (not realy an AC system).

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{aks12}: ACs with revocation.
\item \cite{asm06}: This seems to be the origin of the BBS+ branch of ACs (also,
  probably \cite{aks12} is in this family).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures.
\item \cite{cl11}: ACs from aggregate signatures.
\end{itemize}

@@

>>>>

The ``family'' of AC systems known in the industry as BBS+ originates from
\cite{asm06} (or, probably, from the BBS+ variant in \cite{cdl16b}, which
introduces several improvements). \cite{asm06} presents a GS-like system that
lets users obtain a credential from a Group Manager. This credential is a
BBS+ signature. BBS+ signatures are a digital signature scheme, based on
\cite{bbs04} and following the modification guidelines put forward in
\cite{cl04}\footnote{Essentially, the authors of \cite{asm06} acknowledge
  \cite{cl04} as those who proposed the BBS+ scheme -- but without security
  proofs, which are provided in (the full version of) \cite{asm06}.}. On top
of the signature scheme, they add efficient protocols for obtaining a signature
over a set of committed messages, and proving -- in zero knowledge -- knowledge
of a signature. Users can then be authorized by Application Providers (APs) to
access their services: for this, APs maintain a list of the users they have
granted/revoked access to, using a dynamic accumulator. APs also allow users to
authenticate anonymously up to $k$ times. In order to access the services of APs,
users have to derive a value using a VRF, and further prove that the value used
to seed the VRF is a number within $[1,k]$ -- in addition to, of course, proving
knowledge of a valid BBS+ signature (their credential). APs keep a record of the
accesses. Thus, if a user accesses more than $k$ times a given AP, anyone with
access to the record will be able to learn that a user has accessed more than
$k$ times, as there will be more than one matching VRF-derived values.
Furthermore, these two (or more) values let anyone extract a ``pseudonymous''
identity of the user. The model (only informally presented, formal definitions
appear in \cite{ts06} and proofs are deferred to a full version) seems to be
used in $k$-TAA systems ($k$ Times Anonymous Authentication), and defines
properties for:

\begin{itemize}
\item D-Detectability: Adversaries authenticating more than $k$ times are
  detected.  
\item D-Anonymity: Honest users authenticating less than $k$ times remain
  anonymous.
\item D-Exculpability: No honest user can be framed as having authenticated
  more than $k$ times. The GM cannot be framed as dishonest if that is not
  the case.
\end{itemize}

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{aks12}: BBS+-based ACs with revocation.
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures.
\item \cite{cl11}: ACs from aggregate signatures.
\end{itemize}

@@

\cite{fhs19} has a nice comparison table.
